---
title: "R Notebook"
output: html_notebook
---

# Research Question 2

*Question: What is the effect of different strategies to simultaneously learn one model from multiple TrD’s?*

For answering this question we need to test the effect of the transfer lerning methods (MN, M1, M2, M3, MF) as opposed to the simple model (S) on the score.

## Reading the data

To read the data and create the resevent subset (d) for the current research quetsion.
```{r}
library('ggplot2')
library('emmeans')
data = read.csv('../data/data.csv')
d = subset(data, model %in% c('MN', 'M1', 'M2', 'M3', 'MF', 'S'))
```

## Observing the distribution of scores by models
```{r}
ggplot(d, aes(model, score)) + geom_boxplot(notch = FALSE)
```
We can see that transfer learning's mean performance is better over the simple model (disregarding all the other independent variables and the interaction effects)

```{r}
ggplot(d, aes(score)) + geom_histogram(binwidth = 0.01) + facet_wrap(~model)
```

Let us observe the effect of other independent variables (test dataset) on the score

```{r}
ggplot(d, aes(model, score)) + geom_boxplot(notch = FALSE) + facet_wrap(~TeD)
```
We see that except TeD5 and TeD2, the use of different test datasets and tasks result in observably significant variations in performance in different models.

## Simple Significance Tests
```{r}
m = lm(score ~ model+TeD, d)
summary(m)
confint(m)
```
We see that the choice of TeD has a significant effect on the method score.

### Interaction Effect
Let us observe the interaction effect of the TeD and method.
```{r}
m = lm(score ~ model*TeD, d)
summary(m)
```
We can see that indeed there is significant interaction. We therefore 

# Pairwise comparisons for Models
We need to perform pairwise comparisons while making adjustments for experiment design issues (interaction effects of TeD).
```{r}
m = lm (score ~model*TeD, d)
emmeans(m, ~model)
```

The estimated marginal means(EMMs) tell us that the mean method performance, averaged over the test dataset used, is in the order:
$$ MN > M3 > M2 > M1 > MF > S $$
We can check pairwise comparison for more specifics
```{r}
emmeans(m, pairwise~model)
```
We observe the following:

- using any transfer learning method (Mx) is better than using the simple model (S) i.e. (p < 0.0001).
- Changing method between M1 and M2 (p = 0.5818)  OR M2 and M3 (0.5801) only gives slight improvements.
- using MN over M3 gives marginally significant (p = 0.0500) performance improvement.
- using MN over M1, M2 or MF gives highly significant (p < 0.0001) performance improvement.


## Pairwise comparison per TeD

Lets also account for the performance of models depending on different tasks (TeD).

**Means for particular TeDs**
```{r}
emmeans(m, pairwise~model|TeD)$emmeans
```


**Comtrasts for particular TeDs**
```{r}
emmeans(m, pairwise~model|TeD)$contrasts
```

### For TeD1 (Classification task)
Looking simply at means
$$ M3 > M1 > M2 > MN > MF > S $$

- There is significant differenc by moving from S to Mx (p < 0.0001)
- MN, M1, M2, M3 are result in quite similar performance (p = [1.0, 0.0578] )
- Only for this task MN performs worse than M1, M2, M3. But judging by previous point this is not too significant.


### For TeD2 (Classification task)
Looking simply at means
$$ MN > M3 > M1 > M2 > MF > S $$
-

### For TeD3 (Classification task)
Looking simply at means
$$ MN > M3 > M2 > M1 > MF > S $$


### For TeD4 (Classification task)
Looking simply at means
$$ MN > M2 > M1 > M3 > S > F $$


### For TeD5 (Recommendation task)
Looking simply at means
$$ MN > M3 > M2 > M1 > MF > S $$


### For TeD6 (Regression task)
Looking simply at means
$$ MN > M2 > M1 > M3 > MF > S $$


### For TeD7 (Regression task)
Looking simply at means
$$ MN > M3 > M2 > M1 > MF > S $$





